---
title: "Regular expressions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Regular expressions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(stringrb)
```

Regular expressions are a concise and flexible tool for describing patterns in 
strings. This vignette describes the key features of stringrb's regular 
expressions, as implemented in base R. It is not a tutorial, so if you're unfamiliar regular expressions, try starting at <http://r4ds.had.co.nz/strings.html>. 
If you want to master the details, try reading the classic 
[_Mastering Regular Expressions_](https://amzn.com/0596528124) by 
Jeffrey E. F. Friedl. 

Perl compatible regular expressions are the default pattern engine in stringrb. 
That means when you use a pattern matching function with a bare string, 
it's equivalent to wrapping it in a call to `perl()`:

```{r, eval = FALSE}
# The regular call:
str_extract(fruit, "nana")
# Is shorthand for
str_extract(fruit, perl("nana"))
```

You will need to use `regex()` explicitly if you want to override the default options, as you'll see in examples below.

## Basic matches

The simplest patterns match exact strings:

```{r}
x <- c("apple", "banana", "pear")
str_extract(x, "an")
```
