---
title: "Introduction to stringrb"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to stringrb}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(stringrb)
```

## Pattern matching

The vast majority of stringrb functions work with patterns. These are 
parameterised by the task they perform and the types of patterns they match.

### Tasks

Each pattern matching function has the same first two arguments, a character 
vector of strings to process and a single pattern to match. stringr provides 
pattern matching functions to detect, locate, extract, match, replace, and 
split strings. I’ll illustrate how they work with some strings and a regular 
expression designed to match (US) phone numbers:

```{r}
strings <- c(
  "apple", 
  "219 733 8965", 
  "329-293-8753", 
  "Work: 579-499-7527; Home: 543.355.3679"
)
phone <- "([2-9][0-9]{2})[- .]([0-9]{3})[- .]([0-9]{4})"
```

-   `str_extract()` extracts text corresponding to the **first** match, 
    returning a character vector. `str_extract_all()` extracts all matches and 
    returns a list of character vectors.

    ```{r}
    # What are the phone numbers?
    str_extract(strings, phone)
    #str_extract_all(strings, phone)
    #str_extract_all(strings, phone, simplify = TRUE)
    ```
